An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-12 EconGrowth2.Rnw
Deleted two lines.
Lattice graphs contain only Q predictions. CES lattice graph contains all nestings.

**** Need to strip out $x$ and $u$ predictions ****

<<CD_GDP_Lattice_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
createCDLatticeGraph()
@

@@

<<CESq_ternary_graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values, ($le$)$k$ nesting.">>=
cesResampleTrianglePlot(energyType="Q", nest="(kl)e")
@

@@

Figure~\ref{fig:CES_GDP_Lattice_Graph_kle} compares CES model predictions 
to historical data for the $(kl)e$ nesting.

**** Matt: Remove $x$ and $u$ lines. Replace with lines for each nesting. ****

<<CES_GDP_Lattice_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($kl$)$e$ nesting.">>=
createCESLatticeGraph(nest="(kl)e")
@

Figure~\ref{fig:CES_GDP_Lattice_Graph_lek} compares CES model predictions 
to historical data for the $(le)k$ nesting.

<<CES_GDP_Lattice_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($le$)$k$ nesting.">>=
createCESLatticeGraph(nest="(le)k")
@

Figure~\ref{fig:CES_GDP_Lattice_Graph_ekl} compares CES model predictions 
to historical data for the $(ek)l$ nesting.

<<CES_GDP_Lattice_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($ek$)$l$ nesting.">>=
createCESLatticeGraph(nest="(ek)l")
@

@@

Figure~\ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.
**** Remove $x$ and $u$ lines. ****

<<LINEX_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
createLINEXLatticeGraph()
@

>>>>

<<CD_GDP_Lattice_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
createCDLatticeGraph(energyType="Q")
@

@@

<<CESq_ternary_graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values, ($le$)$k$ nesting.">>=
cesResampleTrianglePlot(energyType="Q", nest="(le)k")
@

@@

Figure~\ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions 
to historical data for all nestings.

<<CES_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models.">>=
createCESLatticeGraph(energyType="Q")
@

@@

Figure~\ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.

<<LINEX_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
createLINEXLatticeGraph(energyType="Q")
@
